---
title: "R Notebook"
output: html_notebook
---

# Yara Mohammadi - 880199265

# 3- 
### C.

```{r}


p_even = 0.5 * (1 + exp(-20))
p_even
```


# 8-

### Loading the dataset

```{r}
foods <- read.csv(file = 'Foods.csv')
head(foods)
```

### <b> A. <\b>

By changing the number of bins, we could control how close the count axis for histogram is to the density function. 

```{r}
library(ggplot2)


ggplot(foods, aes(x=pricePerServing, y=..count..)) + scale_x_log10() + geom_histogram(fill='palegreen4', col='green', bins = 20) + ggtitle("Histogram & Density of pricePerServing") + geom_density(col='red') + xlab('Price Per Serving (Logarithmic)')
   
```

### <b> B. <\b>

```{r}
ggplot(foods, aes(x=readyInMinutes, y=healthScore, alpha = ..level..)) + stat_density2d(geom = "polygon", col='white', fill='palegreen4') + ggtitle("Your Title Goes Here") + xlab('Ready In Minutes') + ylab('Health Score')
```

### <b> C. <\b>


```{r}

# Sort dishType  in ascending order
foods2 =  as.data.frame(sort(table(foods$dishType)))

ggplot(foods2, aes(x=Var1, y=Freq, fill=Var1)) + geom_bar(stat='identity') + coord_flip() + xlab('Dish Type') + ylab('Count') + theme(legend.position = "none") + ggtitle("Horizontal Bar Plot of Dish Types")
```

### <b> D. <\b>


```{r}
ggplot(foods, aes(x=dishType, y=healthScore, fill=dishType)) + geom_boxplot() + xlab('Dish Type') + ylab('Health Score') + theme(legend.position = "none") + ggtitle("Boxplots of Health Bills")
```

### <b> E. <\b>

For this question, I used the GGmosaic library on top of GGplot. Mosaic plots can be crafted by BarPlots as well. 

To obtain the percentages, I created a new column in the Foods dataset to measure them first and then placed the measured numbers in the geom_text() function.
```{r}
library(ggmosaic)
library(dplyr)

foods <- foods %>%
  count(veryHealthy, dairyFree) %>%       
  group_by(veryHealthy) %>%
  mutate(pct= prop.table(n))
  ggplot(foods) + 
  geom_col() +
  aes(x=veryHealthy, y=pct, fill=dairyFree) +
  geom_text(aes(label=paste0(sprintf("%1.1f", pct*100),"%")), position=position_stack(vjust=0.5)) + 
  labs(title='Mosaic Plot of VeryHealthy & DairyFree', fill = "dairy Free") + ylab('Proportion') + xlab('Very Healthy') + theme()

```
